---
title       : Make your own airquality model    
subtitle    : A shiny app
author      : Sebastien Viaene
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny]            # {mathjax, quiz, bootstrap, shiny}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Context

The quality of the outside air is vital to public health. Ozone is one of the metrics that influences the quality of the air.

- Need active monitoring of ozone
- Need additional weather metrics
- Need to build thrustworthy predictions for ozone levels
- Need public awereness of what influences air quality

--- .class #id 

## A shiny web application

A simple web application to demonstrate the weather influence on ozone levels:

https://sviaene.shinyapps.io/shiny/

- Data: New York Air Quality Measurements (standard R dataset)
- Possible input: Solar radiation, wind, temperature, month (i.e. seasonal variability)
- Model: A generalized linear model to predict Ozone from the chosen parameters
- Output: Model vs observations plot and average deviation

--- .class #id 

## Input

- Interactive checkbox to choose which parameters to use in the model
- Update model button to start/update the actual modelling

```{r opts.label = 'shiny', echo=FALSE}
slidifyUI(
  sidebarPanel(
          checkboxInput('Solar.R', 'Solar radiation', TRUE),
          checkboxInput('Wind', 'Wind', FALSE),
          checkboxInput('Temp', 'Temperature', FALSE),
          checkboxInput('Month', 'Month', FALSE),
          
          actionButton("update", "Update model")
  ),
  mainPanel(
  )
)

```

--- &twocol w1:50% w2:50%
### Output examples
*** =left

```{r echo=FALSE}

library(datasets)
airData <- airquality[complete.cases(airquality),]
modelData <- data.frame(airData$Ozone)
names(modelData) <- "Ozone"

modelData <- cbind(modelData, airData$Solar.R)
model <- glm(Ozone ~ ., data = modelData)

predictions <- predict(model, newdata = modelData)
mean_dev <- sqrt(mean((modelData$Ozone - predictions)^2))

plot(modelData$Ozone ~ predictions, 
     main="Model using only solar radiation", 
     ylab = "Observed Ozone (ppb)", xlab="Model Ozone prediction (ppb)",
     xlim=c(-10, 150), ylim=c(-10,150))
abline(a=0, b=1)
text(100,0,labels = paste("Average deviation:",round(mean_dev, digits = 1)))
                
```

*** =right

```{r echo=FALSE}

library(datasets)
airData <- airquality[complete.cases(airquality),]
modelData <- data.frame(airData$Ozone)
names(modelData) <- "Ozone"

modelData <- cbind(modelData, airData$Solar.R)
modelData <- cbind(modelData, airData$Wind)
modelData <- cbind(modelData, airData$Temp)

model <- glm(Ozone ~ ., data = modelData)

predictions <- predict(model, newdata = modelData)
mean_dev <- sqrt(mean((modelData$Ozone - predictions)^2))

plot(modelData$Ozone ~ predictions, 
     main="Model using solar radiation, wind and temperature", 
     ylab = "Observed Ozone (ppb)", xlab="Model Ozone prediction (ppb)",
     xlim=c(-10, 150), ylim=c(-10,150))
abline(a=0, b=1)
text(100,0,labels = paste("Average deviation:",round(mean_dev, digits = 1)))
                
```






